NIRCam Faint and Bright Flux Calibration Plan

### 2017-07-05 ms.tex
re-ordered the author list to push George higher up
added some details about the shorter flux ladder using P330-E.

\author{E. Schlawin, Jarron Leisenring, M. Rieke, G. Rieke, K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

@@

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event.

\begin{figure}[!t]
\centering
\includegraphics[width=.55\columnwidth]{flux_ladder.pdf}
\caption{Schematic sensitivity ladder going from an MSX standard (with a sub-array, neutral density filter observation) to a faint JWST standard (with a full array, full throughput observation).
An intermediate standard can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
\end{figure}

@@

\subsection{Using intermediate Standards to Check the Flux Ladder}

@@

However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to full frame imaging in a narrowband mode in one step by using an intermediate JWST standard.
To begin, the F212N filter could be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
If the F212N filter is used to image P330-E with a full frame direct imaging mode, it is just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
The F212N filter is chosen since there are few stellar absorption lines in this filter.
The advantage with this single transfer from an MSX standard to a full frame P330-E image is that it fewer steps than the ladder described above.
The disadvantage is that there would be a large disparity in detector well depth between the vertical and horizontal steps on this ladder.
If flux calibration time is available, this alternative flux ladder or simply the ``offshoot'' would serve as a check on the conversion from faint to bright targets.

>>>>

\author{E. Schlawin, G. Rieke, Jarron Leisenring, M. Rieke, K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

@@

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event as the reference sphere.

\begin{figure}[!t]
\centering
\includegraphics[width=.8\columnwidth]{flux_ladder.pdf}
\caption{Schematic sensitivity ladder going from an MSX standard (with a sub-array, neutral density filter observation) to a faint JWST standard (with a full array, full throughput observation).
Each observation step is labeled in the bottom corner of each image schematic.
An intermediate standard (shown with green connecting arrows) can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
\end{figure}

@@

\subsection{Using Intermediate Standards to Check the Flux Ladder}

@@

However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to full frame imaging in a narrowband mode in 3 steps by using an intermediate JWST standard.
This shorter ladder is illustrated in Figure \ref{fig:sensitivityLadderP330E}.
To begin, the F212N filter would be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
If the F212N filter is used to image P330-E with a full frame direct imaging mode, it is just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
The F212N filter is chosen since there are few stellar absorption lines in this filter.
The advantage with this single transfer from an MSX standard to a full frame P330-E image is that it fewer steps than the ladder described above.
The disadvantage is that there would be a large disparity in detector well depth between the steps on this ladder.
If flux calibration time is available, this alternative flux ladder or simply the ``offshoot'' would serve as a check on the conversion from faint to bright targets.

\begin{figure}[!t]
\centering
\includegraphics[width=.32\columnwidth]{flux_ladder_p330e.pdf}
\caption{Schematic of an alternative sensitivity ladder to Figure \ref{fig:sensitivityLadder}.
This ladder would use the intermediate-brightness JWST standard P330-E (G2~V type) to transfer from an MSX star to full frame imaging in a narrowband filter.
The observing time needed for step 2 is considerable, but if allocated (7.5 hr to get SNR=200), this provides a way to calibrate full frame imaging with fewer transfers than the 6 step method above.
The disadvantage of this method is that each step involves a large disparity in well depths.}\label{fig:sensitivityLadderP330E}
\end{figure}
